Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Update main.tex
modify introduction

For our project, we intend to ...

@@

\paragraph{Prompting techniques}. A prompt is a command a user gives to a generative LLM used to guide its output for a downstream task, which contains several of the following: a role (persona) the LLM has to follow (e.g. "You are a helpful assistant"), a precise task description, examples (exemplars) for analogous learning (few-shot prompting), requirements on the process of reasoning, style instructions, output format requirements, additional information for in-context learning, emotion prompting components (highlighting why the task or a particular requirement is important). Prompts can be combined into sequences or graphs (with complex branching and parallelism). Of particular interest are small requirements on the reasoning process that can significantly improve performance when added to the prompt, such as "Rephrase and expand the question, and respond" \cite{}, or "Let’s think step by step" \cite{kojima2022}. Chain-of-thought prompts improve reasoning capabilities by asking the model to speak its process of thinking out loud, with variations including self-ask, step-back prompting, thread-of-thought, least-to-most prompting (decomposing then solving), plan-and-solve prompting, tree-of-thought, recursion-of-thought and many more \cite{schulhoff2024prompt}. 
%with the resulting systems possibly using multiple CoT reasoning trajectories to select the most likely one (e.g. Uncertainty-Routed CoT Prompting, or making an LLM generate various prompting instructions that are then tested by another LLM on 24 NLP tasks to chose the best one \cite{zhou2022large}). %katja: I omit this to save space as not directly relevant
Furthermore, prompts themselves can be compressed and automatically optimized to improve efficiency and reduce costs \cite{chang2024efficient}. \cite{ge2023context} compress a long context 4x into memory slots, while \cite{weston2023system} ask the LLM to first summarize the prompt and then execute it. Self-criticism and ensembling techniques can further be used to improve reasoning capabilities \cite{schulhoff2024prompt}.

@@

\paragraph{Dataset}
We plan to use the ScienceQA dataset. ScienceQA is a multimodal dataset containing science questions and their answers.

>>>>

For our project, we intend to compare different approaches around generative large language models to generate solutions for school science problems. On an existing benchmark with human solutions, we are planning to compare: a pure LLM with zero-shot and few-shot prompting (and possibly some more fine-grained prompting techniques), an agentic approach with ability to query external resources like textbooks in physics, maths etc, and soft-prompting techniques. We then plan to attempt knowledge distillation to a smaller LLM.

@@

\paragraph{Prompting techniques}. A prompt is a command a user gives to a generative LLM used to guide its output for a downstream task, which contains several of the following: a role (persona) the LLM has to follow (e.g. "You are a helpful assistant"), a precise task description, examples (exemplars) for analogous learning (few-shot prompting), requirements on the process of reasoning, style instructions, output format requirements, additional information for in-context learning, emotion prompting components (highlighting why the task or a particular requirement is important). Prompts can be combined into sequences or graphs (with complex branching and parallelism). Of particular interest are small requirements on the reasoning process that can significantly improve performance when added to the prompt, such as 
%"Rephrase and expand the question, and respond" \cite{}, or 
"Let’s think step by step" \cite{kojima2022large}. 
Chain-of-thought prompts improve reasoning capabilities by asking the model to speak its process of thinking out loud, with variations including self-ask, step-back prompting, thread-of-thought, least-to-most prompting (decomposing then solving), plan-and-solve prompting, tree-of-thought, recursion-of-thought and many more \cite{schulhoff2024prompt}. 
%with the resulting systems possibly using multiple CoT reasoning trajectories to select the most likely one (e.g. Uncertainty-Routed CoT Prompting, or making an LLM generate various prompting instructions that are then tested by another LLM on 24 NLP tasks to chose the best one \cite{zhou2022large}). %katja: I omit this to save space as not directly relevant
Furthermore, prompts themselves can be compressed and automatically optimized to improve efficiency and reduce costs \cite{chang2024efficient}. \cite{ge2023context} compress a long context 4x into memory slots, while \cite{weston2023system} ask the LLM to first summarize the prompt and then execute it. Self-criticism and ensembling techniques can further be used to improve reasoning capabilities \cite{schulhoff2024prompt}.

@@

\paragraph{Dataset}
We plan to use the ScienceQA dataset \cite{lu2022learn}. ScienceQA is a multimodal dataset containing science questions and their answers.
